%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Staff Software Engineer, Node} % Job title
    {Google} % Organization
    {Sunnyvale, CA} % Location
    {Nov. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, led, and implemented successful Dev Entry program to create a stable CI/CD pipeline for GPU, improving signal to noise from 25\% to 90\% and now working with leadership to extend to all VM families}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer, Cloud Engprod} % Job title
    {} % Organization
    {} % Location
    {Nov. 2021 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Significantly enhanced DevCluster infrastructure and resource efficiency: saved >100 machines, added E2 support for all single-node pools, delivered a 10x reduction in SSH issues for Persistent Disk, and fully landed the DevCluster BYOVM solution to accelerate NPI development}
        \item {Led the strategic transition of DevCluster support to the Warsaw team, co-authoring the transition plan, providing in-person training, and offering critical support for urgent issues (eg. CBF Code Red, Windows 11 Freeze P0), ensuring no reliability degradation}
        \item {Architected and prototyped a solution to catch critical production turnup issues; provided data that led to successful concept entry and laid the groundwork for successor CY projects (eg. Staging-cycling).}
        \item {Designed and implemented a bug enhancement tool which reduces MTTR of turnup SLO violations by enriching bugs with key information using Machine Learning and data transformation}
        \item {Built a real-time vector database solution, achieving 90\% precision for some nodes and designing a 2-phase embedding solution to improve precision from 64\% to 88\% for all other nodes}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer, Cloud Engprod} % Job title
    {} % Organization
    {} % Location
    {May 2018 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Prevented approximately 2 breakages per month and 60\% of DevCluster-wide outages by making DevClusters hermetic}
        \item {Improved developer setup velocity by 100x and reduced flakiness through proxy standardization; led deprecation of Vanilla DevCluster, reclaiming 100 DevCluster's worth of resources and reducing on-call load}
        \item {Unblocked hundreds of engineers and critical revenue streams (over \$300M TDB) by enabling CloudTop support and Pantheon development}
        \item {Revamped the DevCluster feature engagement process, establishing clear ownership and pathways for sustainable growth and partner self-service including the design/implementation of multi-user DevClusters for easy collaboration}
        \item {Led critical initiatives (Project Phoenix, Chubby Sharding, Golden DevCluster) reducing Spanner abuse by 40x, improving DevCluster stability (97\% test Chubby usage reduction), and protecting 90\% of components}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Google • Cloud} % Job title
    {Internships} % Organization
    {} % Location
    {Jan. 2017 - April 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved log processing performance by over 98\% and reduced data input by 96\% via preprocessing and contributions to Google Golang ecosystem}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {InsightSquared • Marketing and Sales Analytics} % Job title
    {} % Organization
    {} % Location
    {Jan. 2016 - June 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved application performance up to 95\% speed increase and 99.9\% memory reduction; created 5 new sales and marketing reports integral to core product, used daily by hundreds of teams}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intuit • Payment and Filing Group} % Job title
    {} % Organization
    {} % Location
    {Jan. 2015 - June 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recognized by the EVP with a monetary award for using cutting edge technologies to reduce page complexity and simplify user experience by 75\%}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {United Technologies • Customer Response Center} % Job title
    {} % Organization
    {} % Location
    {May 2014 - Aug. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Saved over 1900 hours/year for hundreds of internal/external contacts by designing and developing the CRC website and alerting}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
